Designing Types for R, Empirically

### 2020-05-15 paper/main.tex
Add graph

>>>>

\begin{figure}[!h]  \centering
  \includegraphics[width=\linewidth]{plots/function_polymorphism.pdf}
  \caption{Function Polymorphism}\label{fig:funpoly}
\end{figure}

Figure shows the distribution of functions against the number of polymorphic
positions. We observe that \PercMonomorphicFunctions
(\CountMonomorphicFunctions) functions are monomorphic. The remaining
\PercPolymorphicFunctions (\CountPolymorphicFunctions) have at least one
polymorphic parameter or return type. Polymorphic functions are spread
across many packages, \CountMonomorphicPackages out of the 412 packages from our
corpus export only monomorphic functions.
